IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-07-08 paper/real.tex
Minor touchups
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

In this section, we describe these two implementations.  Furthermore,
we consider how our formalism could be applied to the C programming
language, and connect it to a previous IFC system for Haskell.
%
Our goal is to show the flexibility of the embedding in settings with
vastly different properties, as well as to discuss the
semantic gap that must be overcome in some cases to apply our formalism
to other systems.
%
%% Two of the systems we describe have been implemented: the Haskell
%% system~\cite{lio} and the COWL~\cite{swapi} system; we leave the
%% implementation of the IFC system for C to future work.

@@

However, this issue of performance and JavaScript isolation is not
unique to our work, and has been solved by browser engines,
which
rely on the isolation of content from
different origins (e.g., two iframes of different origins) to
implement the same-origin policy.
%
Since creating an OS thread for each iframe is expensive, both
Google's V8 and Mozilla's SpiderMonkey provide a means for running
JavaScript code in isolation in a single OS thread,
on disjoint sub-heaps.
%
In V8, this unit of isolation is called a \emph{context}~\tocite{}; in
SpiderMonkey, it is called a \emph{compartment}~\tocite{}.
%
Each context/compartment is associated with a global object, which, by
default, implements the JavaScript standard library (e.g.,
\verb|Object|, \verb|Array|, etc.).
%
Naturally, our notion of a task for JavaScript directly corresponds to
a context/compartment.

When JavaScript is embedded in web browser engines, such as Google's
Blink or Mozilla's Gecko, or in server-side platforms such as Node.js,
additional APIs such as the Document Object Model (DOM) or the file
system get exposed as part of the runtime system.
These features are exposed by extending the global object, just like
for the standard library.  For this reason, it is easy to modify
these systems to remove arbitrary external effects when implementing
an IFC system, and reintroducing important effects in a safe manner.

@@

\begin{figure}
\centerline{\includegraphics[width=\columnwidth]{figs/node}}
\caption{\label{fig:node} Retrofitting Node.js JavaScript with IFC.
This example shows how our trusted monitor (left) is used to mediate
communication between two tasks for which IFC is enforced (right).}
\end{figure}
%
All IFC primitives are mediated by the trusted library code (executing
as the main Node.js context), which tracks the current label, messages,
etc.\ of each task.  An example for |send|/|recv| is shown in
Figure~\ref{fig:node}.

%While V8 provides a means for sharing any object between contexts (used
%by same-origin contexts in Blink),
Our system conservatively restricts
the kinds of messages that can be exchanged by tasks by
only allowing string values to be exchanged via |send| (and |sandbox|).
%
In our formalization, this amounts to restricting the IFC language rule
for |send| in the following way:
%{
\newcommand{\str}{"string"}
%format tOf (e) = "\texttt{typeOf}("e")\texttt{ === \str}"
%format ttrue = "\texttt{true}"
\begin{mathpar}
\inferrule[JS-send]
{
|il canFlowTo il'|\\
|iS(id') = Q|\\
|iS' = iS [ mapsto id' (il', id,  iv) , Q ]|\\
|ie = IT te|\\
|conf tS (tOf te) -> conf tS ttrue|
}
{|
iconf iS (fullconf id il tS (iniEi (send id' il' iv)), ldots)
.->
iS'; sched step (fullconf id il tS (iniEi unit), ldots)
|}
\end{mathpar}
%}
%
For convenience, we have implemented a library that provides
more flexible primitives, which, among other things,
automatically marshalls JSON objects to/from strings on each
|send|/|recv|.

While the described system implements |specLangJS seqf|, server-side
applications may require access to the file system, HTTP server, HTTP
client, etc.
%
Unfortunately, our formalism does not capture such external effects
and exposing the Node.js libraries directly to sandboxed tasks is unsafe.
%
We, instead, implement libraries such as a labeled file system as
message exchanges between the sandboxed tasks (e.g., \textsf{task-1}
in Figure~\ref{fig:node}) and the main Node.js task that implements
our IFC monitor.\footnote{
  Importantly, we provide mostly-identical interfaces to
  the standard Node.js libraries, hiding the underlying
  message-passing implementations.
}
%
(This is safer than the approach of simply wrapping objects, which can
potentially allow for accessing objects outside the context.)
%
This task is trusted to ensures that, for instance, labels are
propagated to files and the labels of the task performing the
operations and the file in question are inspected appropriately, as to
preserve non-interference.
%
Unfortunately, while imposing such a proof burden on the
framework developer is undesirable, this is also somewhat expected:
different language environments expose different libraries for
handling external I/O.
%
For instance, in the case of Node.js, how labels interact with the
file system may even vary according to the application (e.g.,
different from our implementation, Hails~\cite{hails} does not persist
labels).
%
While we can extend our formalism to model a particular interface to
the file system, HTTP client, etc. the applicability of this are
unclear and left to future work.
%

@@

Simply disallowing all external effects for all browsing contexts is
overly-restricting; pages typically load images, perform XHR requests,
etc.
%
Hence, rather than disallowing all external effects, COWL allows
controlled network communication (inter-frame communication is
dictated by our |send| rule) by associating an implicit label with a
remote host: namely the label corresponding to its origin.
%
In turn, when a task perform a request, the COWL runtime performs the
same label check as that of |send|, e.g., does the task label flow to
the remote origin label.
%
While the external effects of COWL can be formally modeled, and indeed
necessary, we do not model these effects in our more general
framework, since, like for Node.js case, this is a platform-specific
detail.
%
Indeed, even the labeled HTTP client in  Node.js and COWL differ, even
though they're both JavaScript systems, simply because of the
different environment.

>>>>

In this section, we describe these two implementations.  Furthermore,
we consider how our formalism could be applied to the C programming
language and connect it to a previous IFC system for Haskell.
%
The goal of this section is to show the flexibility of the embedding in settings with
vastly different properties and discuss the
semantic gap that must be overcome to apply our formalism
to other systems.
%
%% Two of the systems we describe have been implemented: the Haskell
%% system~\cite{lio} and the COWL~\cite{swapi} system; we leave the
%% implementation of the IFC system for C to future work.

@@

However, this issue of performance and JavaScript isolation is not
unique to our work and has been solved by browser engines,
which also
rely on the isolation of content from
different origins (e.g., two iframes of different origins) to
implement the same-origin policy.
%
Since creating an OS thread for each iframe is expensive, both
Google's V8 and Mozilla's SpiderMonkey provide a means for running
JavaScript code in isolation in a single OS thread,
on disjoint sub-heaps.
%
In V8, this unit of isolation is called a \emph{context}; in
SpiderMonkey, it is called a \emph{compartment}.
%
Each context/compartment is associated with a global object, which, by
default, implements the JavaScript standard library (e.g.,
\verb|Object|, \verb|Array|, etc.).
%
Naturally, our notion of a task for JavaScript directly corresponds to
a context/compartment.

When JavaScript is embedded in web browser engines, such as Google's
Blink or Mozilla's Gecko, or in server-side platforms such as Node.js,
additional APIs such as the Document Object Model (DOM) or the file
system get exposed as part of the runtime system.
These features are exposed by extending the global object, just like
for the standard library.  For this reason, it is easy to modify
these systems to remove arbitrary external effects when implementing
an IFC system so important effects can be reintroduced in a safe manner.

@@

\begin{figure}
\centerline{\includegraphics[width=\columnwidth]{figs/node}}
\caption{\label{fig:node} Retrofitting Node.js JavaScript with IFC.
This example shows how our trusted monitor (left) is used to mediate
communication between two tasks for which IFC is enforced (right).}
\end{figure}
%
All IFC primitives are mediated by the trusted library code (executing
as the main Node.js context), which tracks the current label, messages,
etc.\ of each task.  An example for |send|/|recv| is shown in
Figure~\ref{fig:node}.
%While V8 provides a means for sharing any object between contexts (used
%by same-origin contexts in Blink),
Our system conservatively restricts
the kinds of messages that can be exchanged by tasks by
only allowing string values to be exchanged via |send| (and |sandbox|).
%
In our formalization, this amounts to restricting the IFC language rule
for |send| in the following way:
%{
\newcommand{\str}{"string"}
%format tOf (e) = "\texttt{typeOf}("e")\texttt{ === \str}"
%format ttrue = "\texttt{true}"
\begin{mathpar}
\inferrule[JS-send]
{
|il canFlowTo il'|\\
|iS(id') = Q|\\
|iS' = iS [ mapsto id' (il', id,  iv) , Q ]|\\
|ie = IT te|\\
|conf tS (tOf te) -> conf tS ttrue|
}
{|
iconf iS (fullconf id il tS (iniEi (send id' il' iv)), ldots)
.->
iS'; sched step (fullconf id il tS (iniEi unit), ldots)
|}
\end{mathpar}
%}
%
For convenience, we have implemented a library that provides
more flexible primitives, which, among other things,
automatically marshalls JSON objects to/from strings on each
|send|/|recv|.

While the described system implements |specLangJS seqf|, server-side
applications may require access to the file system, HTTP server, HTTP
client, etc.
%
Unfortunately, our formalism does not capture such external effects
and exposing the Node.js libraries directly to sandboxed tasks is unsafe.
%
We, instead, implement libraries such as a labeled file system as
message exchanges between the sandboxed tasks (e.g., \textsf{task-1}
in Figure~\ref{fig:node}) and the main Node.js task that implements
our IFC monitor.\footnote{
  Importantly, we provide mostly-identical interfaces to
  the standard Node.js libraries, hiding the underlying
  message-passing implementations.
}
%
(This is safer than the approach of simply wrapping objects, which can
potentially allow objects to be accessed outside the context.)
%
This task is trusted to ensures that labels are
propagated to files and the labels of the task and the file in question permit
this flow.
%
Unfortunately, while imposing such a proof burden on the
framework developer is undesirable, this is also somewhat expected:
different language environments expose different libraries for
handling external I/O.
%
For instance, in the case of Node.js, how labels interact with the
file system may even vary according to the application (e.g.,
in the IFC system Hails~\cite{hails}, labels are not persisted).
%
While we can extend our formalism to model a particular interface to
the file system, HTTP client, etc. the utility of this formalization is
unclear and left to future work.
%

@@

Simply disallowing all external effects for all browsing contexts is
overly-restricting; pages typically load images, perform XHR requests,
etc.
%
Hence, rather than disallowing all external effects, COWL allows
controlled network communication (inter-frame communication is
dictated by our |send| rule) by associating an implicit label with a
remote host: namely the label corresponding to its origin.
%
In turn, when a task perform a request, the COWL runtime performs the
same label check as that of |send|, e.g., does the task label flow to
the remote origin label.

Once again, while the external effects of COWL can be formally modeled,
we do not model these effects in our more general framework, since, like
for Node.js case, they are a platform-specific
detail.
%
Indeed, even the labeled HTTP client in  Node.js and COWL differ, even
though they're both JavaScript systems, simply because of the
differing environments.
